### 2025-08-04 multiple-regression.qmd
20250803 - edits

Only the quadratic term for target share (not height or weight) shows a significant association.

@@

$$
\begin{aligned}
  \text{fantasy points} \; = \; &\beta_0 + \beta_1 \cdot \text{age} + \beta_2 \cdot \text{age}^2 + \beta_3 \cdot \text{height} + \beta_4 \cdot \text{height}^2 + \\
  &\beta_5 \cdot \text{weight} + \beta_6 \cdot \text{weight}^2 + \beta_7 \cdot \text{target share} + \beta_8 \cdot \text{target share}^2 + \epsilon \\
  = &`r petersenlab::apa(beta0, decimals = 2)` + `r petersenlab::apa(beta1, decimals = 2)` \cdot `r petersenlab::apa(age, decimals = 0)` + `r petersenlab::apa(beta2, decimals = 2)` \cdot `r petersenlab::apa(age, decimals = 0)`^2 + `r petersenlab::apa(beta3, decimals = 2)` \cdot `r petersenlab::apa(height, decimals = 0)` + `r petersenlab::apa(beta4, decimals = 2)` \cdot `r petersenlab::apa(height, decimals = 0)`^2 + \\
  &`r petersenlab::apa(beta5, decimals = 2)` \cdot `r petersenlab::apa(weight, decimals = 0)` + `r petersenlab::apa(beta6, decimals = 2)` \cdot `r petersenlab::apa(weight, decimals = 0)`^2 + `r petersenlab::apa(beta7, decimals = 2)` \cdot `r petersenlab::apa(target_share, decimals = 0)` + `r petersenlab::apa(beta8, decimals = 2)` \cdot `r petersenlab::apa(target_share, decimals = 0)`^2 + \epsilon \\
  = &`r petersenlab::apa(predictedFantasyPoints, decimals = 2)`
\end{aligned}
$$ {#eq-quadraticTermsRegressionModelSubstitute}

>>>>

Only target share (not height or weight) shows a significant association, including its linear and quadratic terms.

@@

$$
\begin{aligned}
  \text{fantasy points} \; = \; &\beta_0 + \beta_1 \cdot \text{age} + \beta_2 \cdot \text{age}^2 + \beta_3 \cdot \text{height} + \beta_4 \cdot \text{height}^2 + \\
  &\beta_5 \cdot \text{weight} + \beta_6 \cdot \text{weight}^2 + \beta_7 \cdot \text{target share} + \beta_8 \cdot \text{target share}^2 + \epsilon \\
  = &`r petersenlab::apa(beta0, decimals = 2)` + `r petersenlab::apa(beta1, decimals = 2)` \cdot `r petersenlab::apa(age, decimals = 0)` + `r petersenlab::apa(beta2, decimals = 2)` \cdot `r petersenlab::apa(age, decimals = 0)`^2 + `r petersenlab::apa(beta3, decimals = 2)` \cdot `r petersenlab::apa(height, decimals = 0)` + `r petersenlab::apa(beta4, decimals = 2)` \cdot `r petersenlab::apa(height, decimals = 0)`^2 + \\
  &`r petersenlab::apa(beta5, decimals = 2)` \cdot `r petersenlab::apa(weight, decimals = 0)` + `r petersenlab::apa(beta6, decimals = 2)` \cdot `r petersenlab::apa(weight, decimals = 0)`^2 + `r petersenlab::apa(beta7, decimals = 2)` \cdot `r petersenlab::apa(target_share, decimals = 1)` + `r petersenlab::apa(beta8, decimals = 2)` \cdot `r petersenlab::apa(target_share, decimals = 1)`^2 + \epsilon \\
  = &`r petersenlab::apa(predictedFantasyPoints, decimals = 2)`
\end{aligned}
$$ {#eq-quadraticTermsRegressionModelSubstitute}
